Dissertation

### 2023-10-17 HTW.qmd
fix html toc

[Link HTW project page](https://tegorman13.github.io/htw/){target="_blank"}

```{r}
pacman::p_load(tidyverse,knitr,kableExtra)

@@

```{r design, echo=FALSE, fig.cap="Experiment Procedure"}
DiagrammeR::grViz("digraph {
graph [layout = dot, rankdir = LR]
# define the global styles of the nodes. We can override these in box if we wish
node [shape = rectangle, style = filled, fillcolor = Linen]
data1 [label = <<b>Varied Training</b>  
<br ALIGN = 'LEFT' /> 800-1000
<br/> 1000-1200
<br/>1200-1400>]
data2 [label = <<b>Constant Training</b>  
<br/> 800-1000 >]
Test1 [label = <<b>Testing - No Feedback</b>  
<br ALIGN = 'LEFT' /> 100-300
<br/> 350-550
<br/>600-800>]
Test2 [label = <<b>Test From Train</b>  
<br ALIGN = 'LEFT' /> 800-1000
<br/> 1000-1200
<br/>1200-1400>]
Test3[label = <<b>Testing -Feedback</b>  
<br ALIGN = 'LEFT' /> 100-300
<br/> 350-550
<br/>600-800>]

# edge definitions with the node IDs
{data1 data2}  -> Test1 -> Test2 -> Test3
}
",width=700,height=250)

>>>>

[Link HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
```{r}
pacman::p_load(tidyverse,knitr,kableExtra)

@@

### 2023-10-17 Manuscript/pre_sections/pre_html.qmd
fix html toc

## Table of contents
<div id="html-toc"></div>
```{=html}
<script>
<!-- document.addEventListener("DOMContentLoaded", function(){ -->
<!--   var toc = document.getElementById("TOC"); -->
<!--   var placeholder = document.getElementById("toc-placeholder"); -->
<!--   if (toc && placeholder) { -->
<!--     placeholder.appendChild(toc); -->
<!--   } -->
<!-- }); -->
document.addEventListener("DOMContentLoaded", function(){
    var tocDiv = document.getElementById("html-toc");
    var headings = document.querySelectorAll('h1, h2, h3'); // adjust if you need more depth
    var tocList = document.createElement("ul");

    headings.forEach(function(heading) {
        var listItem = document.createElement("li");
        var link = document.createElement("a");
        link.textContent = heading.textContent;
        link.href = "#" + heading.id;
        listItem.appendChild(link);

>>>>

## Table of contents
<div id="html-toc"></div>
```{=html}
<script>
<!-- document.addEventListener("DOMContentLoaded", function(){ -->
<!--   var toc = document.getElementById("TOC"); -->
<!--   var placeholder = document.getElementById("toc-placeholder"); -->
<!--   if (toc && placeholder) { -->
<!--     placeholder.appendChild(toc); -->
<!--   } -->
<!-- }); -->

<!-- document.addEventListener("DOMContentLoaded", function(){ -->
<!--     var tocDiv = document.getElementById("html-toc"); -->
<!--     var headings = document.querySelectorAll('h1, h2, h3'); // adjust if you need more depth -->
<!--     var tocList = document.createElement("ul"); -->

<!--     headings.forEach(function(heading) { -->
<!--         var listItem = document.createElement("li"); -->
<!--         var link = document.createElement("a"); -->
<!--         link.textContent = heading.textContent; -->
<!--         link.href = "#" + heading.id; -->
<!--         listItem.appendChild(link); -->

<!--         if (heading.tagName == "H2") { -->
<!--             listItem.style.marginLeft = "20px"; -->
<!--         } else if (heading.tagName == "H3") { -->
<!--             listItem.style.marginLeft = "40px"; -->
<!--         } -->
<!--         tocList.appendChild(listItem); -->
<!--     }); -->

<!--     tocDiv.appendChild(tocList); -->
<!-- }); -->

document.addEventListener("DOMContentLoaded", function(){
    var tocDiv = document.getElementById("html-toc");
    var headings = document.querySelectorAll('h1, h2, h3'); // adjust if you need more depth
    var tocList = document.createElement("ul");

    headings.forEach(function(heading, index) {
        // Create or get the ID for the heading
        if (!heading.id) {
            heading.id = heading.textContent.replace(/[^a-z0-9]+/gi, '-').toLowerCase() + "-" + index;
        }
        var listItem = document.createElement("li");
        var link = document.createElement("a");
        link.textContent = heading.textContent;
        link.href = "#" + heading.id;
        listItem.appendChild(link);
